---
title: "STAT 505 Fall 2022: Homework 1"
subtitle: David Agyemfra Atakora
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
covid19 <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports_us/08-26-2021.csv")
library(dplyr)
covid19
colnames(covid19)
covid19$Province_State
plot(covid19$Deaths)

covid19 %>% group_by(Province_State)


#ggplot(df,aes(x,y))+geom_point(aes(colour=x))


#ggplot2
library(ggplot2)
ggplot(covid19, aes(x = Deaths, y = Province_State)) +
    geom_point(aes(colour=Deaths))
```

# HW1

The purpose of this homework is to make sure that you have all of the proper technology tools installed. 

Answer Q1 using a .RMD file. Then upload that source file and a PDF output file to Github for your submission.

### Q1. 

Download a .CSV file containing up to date information about COVID-19 cases. A file from August 16th (2021) can be downloaded can be at https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports_us/08-16-2021.csv


### a. (4 points)
Use `dplyr` and a `group_by()` statement to summarize the data in some fashion.

### b. (4 points)
Use `ggplot2` to create a figure of the data

### Q2. (2 points)

Make at least one post on the Microsoft Teams app. This could be creating a new channel, adding a comment, etc..

### Q3. (1 points)

What are you most excited about this semester (this class or in general)?

_The use of R and github_ 

### Q4. (1 points)

What are you most worried about this semester (this class or in general)?

_Not being able to make out the best from this semester_

### Q5. (1 point)

What do you hope to learn in this class?

_I want to develop a strong knowledge in Statistical Analysis and modeling. Also, how I can apply statistics to a real life dataset._

### Q6. (1 point)
What degree do you hope to earn from MSU?

_Master of Science in Statistics_

### Q7. (1 point)
What do you hope to do after graduating from MSU?

_I hope to develop a career in Actuarial Science with my Statistics degree being able to make sense from any large datasets._

### Q8. (1 point)
Is there anything else that you want me to know?

_I am ready to learn more from this course; in and out of class._
